\section{Mission Profile}
\subsection{Mission Profile regarding the Structure}
In terms of aircraft maneuverability, the Model 10 Electra was designed to be stable and predictable in flight, with a maximum design load factor of 4.4 g. The aircraft was not intended for aerobatic maneuvers or high-performance flying, but rather for efficient and reliable transportation.

The impact of maneuvering loads on the aircraft structure was carefully considered during the design process, with engineers using advanced stress analysis techniques to ensure that the aircraft could withstand the stresses of normal flight operations. However, as with any aircraft, excessive or sustained high-g maneuvers could potentially cause damage to the structure or lead to fatigue cracking over time.

The maximum speed of the Model 10 Electra was approximately 210 mph (338 km/h), which was considered fast for its time. The materials used in the construction of the aircraft, including aluminum alloy and steel, were chosen for their strength, durability, and resistance to fatigue and corrosion. However, prolonged exposure to high speeds and stresses could still cause wear and tear on the materials, which is why regular inspections and maintenance were necessary to ensure the aircraft remained airworthy.

\subsection{Mission Profile Specific Requirements}

The Lockheed Model 10 Electra is a remarkable aircraft that has been designed to cater to various mission profiles. It is a twin-engine, all-metal monoplane whose design reflects both versatility and elegance. Each mission profile has specific requirements that the Electra has been engineered to meet with true values and performance.

For \textbf{passenger transport}, the Electra's cabin is required to offer ample space and comfortable seating for proper number of passengers. The seats are required to provide maximum comfort, thereby ensuring that passengers arrive at their destination feeling refreshed and relaxed. In addition to this, the cabin's aesthetic design and finishing exude sophistication and class, to make it a preferred choice for business or leisure travel where luxury is a priority.
In practice, the Electra has ample and comfortable space for up to 10 passengers and perfectly meets all the requirements for comfort and sophistication.

When it comes to \textbf{cargo transport}, the Electra is built to deliver. Its  cargo is asked to provide ample space to carry up as much cargo as possible to across long distances. The cargo hold should also be designed to withstand harsh weather conditions, making it ideal for transporting goods across difficult terrain. Additionally, its robust should ensure that heavy machinery and other bulky items are transported safely and securely. In practice, Electra is able to carry 670 lb (304 kg) mail and baggage. If no passengers are carried, the cargo capacity is increased to 1,984 lb (900 kg).

As for \textbf{aerial surveying}, Electra should provide good view of below. In practice, the Electra's sleek design and large windows make it an ideal for such mission. The cockpit offers an unobstructed view of the terrain below, providing an excellent platform for scientific research or environmental monitoring. The aircraft's high-altitude capabilities make it easy to capture detailed images of the landscape from above. This data can then be analysed to gain insights into the environment's changes over time accurately.

In \textbf{search and rescue missions}, time is of the essence. The Electra's endurance and range should be engineered to ensure that it remains in the air for extended periods. In practice, with ith a range of 810 mi (1,300 km, 700 nmi) and the ability to stay airborne for up to 10 hours, the Electra covers vast areas of land and sea, providing much-needed support to search and rescue teams on the ground. Its powerful engines and robust construction, as required make it capable of navigating challenging weather conditions in remote locations.

Finally, when it comes to \textbf{military reconnaissance} operations, not only the requirements of both aerial surveying and search and rescue missions are needed, but also speed and altitude are essential. Moreover, the aircraft should be well navigated and in good condition of communication to make the reconnaissance successful and mean The Electra's ability to reach speeds of up to 210 mph (182 kn, 338 km/h) at 5,000 feet (1,524 m) makes it the perfect aircraft for gathering intelligence on enemy positions and movements. Its advanced navigation and communication systems provide crucial support to military personnel by relaying real-time data from the skies.

In all, the information above is summarize in the Table \ref{tab:mission_profile}.

\begin{sidewaystable}[!htp]
    \centering
    \caption{Mission Profile Specific Requirements}
    \label{tab:mission_profile}
    \resizebox{\textwidth}{!}{\begin{tabular}{ll}\toprule
    Mission Profile                             & 
    Requirements                                                                       \\
    \midrule
    \multirow{3}{*}{Passenger transport}        & (Cabin) offer ample space and comfortable seating for proper number of passenger   \\
                                                & (Seat) provide maximum comfort                                                     \\
                                                & The cabin's aesthetic design and finishing exude sophistication and class          \\
    \midrule
    \multirow{3}{*}{Cargo transport}            & Provide ample space to carry up as much cargo as possible to across long distances \\
                                                & Withstand harsh weather conditions                                                 \\
                                                & Robustness                                                                         \\
    \midrule
    Aerial surveying                            & Provide good view of below                                                         \\
    \midrule
    \multirow{2}{*}{Search and rescue missions} & Long endurance                                                                     \\
                                                & Long range                                                                         \\
                                                \midrule
    \multirow{6}{*}{Military reconnaissance}    & Provide good view of below                                                         \\
                                                & Long endurance                                                                     \\
                                                & Long range                                                                         \\
                                                & Fast speed                                                                         \\
                                                & High operation altitude                                                            \\
                                                & Good and reliable navigation and communication system    \\
    \bottomrule                         
    \end{tabular}}
\end{sidewaystable}